**{shorts}**: An R Package for Modeling Short Sprints

### 2022-07-21 shorts-paper.Rmd
small edits

Short sprints profiling is usually performed by: (1) measuring split times using timing gates (i.e., positioned at various distances, e.g., 5, 10, 20, 30, 40 $m$), or (2) getting a velocity trace using a radar gun. Estimation of MSS and TAU parameters from equation \@ref(eq:velocity-time) is performed in **{shorts}** package for the **R language** [@R-base] using *non-linear least squares regression* implemented in the `nlsLM()` function from the **{minpack.lm}** package [@R-minpack.lm].

@@

There is the additional parameter in the output, TC, that is estimated using the `model_radar_gun()` function. The function of this parameter is explained in the [Problems with time sync with the radar gun] section of this paper.

>>>>

Short sprints profiling is usually performed by: (1) measuring split times using timing gates (i.e., positioned at various distances, e.g., 5, 10, 20, 30, 40 $m$), or (2) getting a velocity trace using a radar gun. Estimation of MSS and TAU parameters from equation \@ref(eq:velocity-time) is performed in **{shorts}** package using *non-linear least squares regression* implemented in the `nlsLM()` function from the **{minpack.lm}** package [@R-minpack.lm].

@@

There is the additional parameter in the output, TC, that is estimated using the `model_radar_gun()` function. The utility of this parameter is explained in the [Problems with time sync with the radar gun] section of this paper.
